### 2023-01-19 doc/src/MSLevel.tex
Fix punctuation typo
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

The value of \z{stopi} is zero unless:
(a)~there is an interrupt that is both pending in \z{sip}/\z{siph}
and enabled in \z{sie}/\z{sieh}, or, if the hypervisor extension is
implemented, both pending in \z{hip} and enabled in \z{hie}; and
(b)~the interrupt is not delegated to a lower privilege level
(by \z{hideleg}, if the hypervisor extension is implemented),
When there is a pending-and-enabled major interrupt for supervisor
level, field IID is the major identity number of the highest-priority
interrupt, and field IPRIO indicates its priority.

>>>>

The value of \z{stopi} is zero unless:
(a)~there is an interrupt that is both pending in \z{sip}/\z{siph}
and enabled in \z{sie}/\z{sieh}, or, if the hypervisor extension is
implemented, both pending in \z{hip} and enabled in \z{hie}; and
(b)~the interrupt is not delegated to a lower privilege level
(by \z{hideleg}, if the hypervisor extension is implemented).
When there is a pending-and-enabled major interrupt for supervisor
level, field IID is the major identity number of the highest-priority
interrupt, and field IPRIO indicates its priority.
